### 2024-05-08 thesis/sections/6.2-re-generation.tex
language analysis

        {1}                           & {2}    & {70,49}                             & {54,73}                             & {7,29}                                   & {70,16}                   & {85,06}                   & {13,06}                   & \textcolor{purple}{11,68} & \textcolor{purple}{32,25} & \textcolor{purple}{34,03} \\
        {1}                           & {10}   & {78,26}                             & {63,33}                             & {3,56}                                   & {68,97}                   & {85,01}                   & {10,85}                   & \textcolor{purple}{12,72} & \textcolor{purple}{32,77} & \textcolor{purple}{33,85} \\
        {1}                           & {16}   & {74,18}                             & {52,21}                             & {5,38}                                   & {71,57}                   & {86,87}                   & {10,72}                   & \textcolor{purple}{13,19} & \textcolor{purple}{33,64} & \textcolor{purple}{33,33} \\
        {1}                           & {50}   & {70,83}                             & \textcolor{purple}{43,56}           & {4,21}                                   & {65,23}                   & {83,11}                   & {12,54}                   & \textcolor{purple}{11,81} & \textcolor{purple}{33,14} & \textcolor{purple}{34,72} \\
        {1}                           & {100}  & {73,18}                             & {52,14}                             & {3,86}                                   & \textcolor{purple}{60,94} & \textcolor{purple}{80,85} & \textcolor{purple}{20,36} & \textcolor{purple}{13,67} & \textcolor{purple}{33,71} & \textcolor{purple}{33,64} \\
        {2}                           & {2}    & {72,31}                             & {50,42}                             & {5,52}                                   & {66,2}                    & {83,39}                   & {14,42}                   & \textcolor{purple}{13,32} & \textcolor{purple}{33,62} & \textcolor{purple}{32,73} \\
        {2}                           & {10}   & {75,22}                             & {58,4}                              & {3,99}                                   & {73,22}                   & {87,68}                   & {9,03}                    & \textcolor{purple}{12,37} & \textcolor{purple}{33,3}  & \textcolor{purple}{34,11} \\
        {2}                           & {16}   & {\textbf{81,64}}                    & {\textbf{73,66}}                    & {\textbf{2,86}}                          & {73,44}                   & {88,21}                   & {8,85}                    & \textcolor{purple}{12,98} & \textcolor{purple}{33,94} & \textcolor{purple}{34,24} \\
        {2}                           & {50}   & {74,39}                             & {48,53}                             & {3,17}                                   & {\textbf{75,35}}          & \textbf{88,77}            & \textbf{8,07}             & \textcolor{purple}{14,19} & \textcolor{purple}{33,04} & \textcolor{purple}{33,46} \\
        {2}                           & {100}  & {74,09}                             & {54,88}                             & {3,65}                                   & \textcolor{purple}{54,56} & \textcolor{purple}{76,95} & \textcolor{purple}{22,57} & \textcolor{purple}{13,28} & \textcolor{purple}{32,8}  & \textcolor{purple}{33,38} \\
        {3}                           & {2}    & {71,03}                             & {50,76}                             & {4,62}                                   & {65,18}                   & \textcolor{purple}{82,68} & {14,23}                   & \textcolor{purple}{12,76} & \textcolor{purple}{33,58} & \textcolor{purple}{33,64} \\
        {3}                           & {10}   & {76,91}                             & {59,42}                             & {2,6}                                    & {71,66}                   & {87,14}                   & {9,9}                     & \textcolor{purple}{12,54} & \textcolor{purple}{32,75} & \textcolor{purple}{33,85} \\
        {3}                           & {16}   & {79,95}                             & {67,55}                             & {3,17}                                   & \textcolor{purple}{50,13} & \textcolor{purple}{73,24} & {24,22}                   & \textcolor{purple}{12,93} & \textcolor{purple}{33,79} & \textcolor{purple}{34,46} \\
        {3}                           & {50}   & {62,93}                             & {48,03}                             & {16,58}                                  & {\textbf{76,09}}          & {\textbf{88,5}}           & \textbf{9,2}              & \textcolor{purple}{13,67} & \textcolor{purple}{33,73} & \textcolor{purple}{34,29} \\
        {3}                           & {100}  & {75,74}                             & {57,51}                             & {2,43}                                   & {69,7}                    & {86,14}                   & {9,38}                    & \textcolor{purple}{13,02} & \textcolor{purple}{33,64} & \textcolor{purple}{34,2}  \\
        {4}                           & {2}    & \textcolor{purple}{41,23}           & \textcolor{purple}{42,53}           & \textcolor{purple}{35,33}                & {63,93}                   & \textcolor{purple}{82,34} & {15,3}                    & \textcolor{purple}{12,2}  & \textcolor{purple}{33,25} & \textcolor{purple}{33,64} \\
        {4}                           & {10}   & {78,99}                             & {66,4}                              & {2,08}                                   & {73,22}                   & {88,01}                   & {10,85}                   & \textcolor{purple}{12,5}  & \textcolor{purple}{33,55} & \textcolor{purple}{33,16} \\
        {4}                           & {16}   & {\textbf{80,08}}                    & {\textbf{70,48}}                    & {\textbf{3,47}}                          & {69,4}                    & {86,09}                   & {10,63}                   & \textcolor{purple}{11,72} & \textcolor{purple}{33,1}  & \textcolor{purple}{34,03} \\
        {4}                           & {50}   & {75,48}                             & {54,44}                             & {3,34}                                   & {71,35}                   & {86,61}                   & {10,68}                   & \textcolor{purple}{11,81} & \textcolor{purple}{33,18} & \textcolor{purple}{34,33} \\
        {4}                           & {100}  & {74,78}                             & {57,09}                             & {3,86}                                   & \textcolor{purple}{59,2}  & \textcolor{purple}{80,14} & \textcolor{purple}{20,57} & \textcolor{purple}{12,67} & \textcolor{purple}{32,3}  & \textcolor{purple}{34,55} \\
        {6}                           & {2}    & {72,87}                             & {51,44}                             & {2,78}                                   & {60,82}                   & \textcolor{purple}{80,42} & {17,07}                   & \textcolor{purple}{13,45} & \textcolor{purple}{33,73} & \textcolor{purple}{33,64} \\
        {6}                           & {10}   & {73,61}                             & {48,73}                             & {2,82}                                   & \textcolor{purple}{32,64} & \textcolor{purple}{58,42} & \textcolor{purple}{33,12} & \textcolor{purple}{11,89} & \textcolor{purple}{33,15} & \textcolor{purple}{35,03} \\
        {6}                           & {16}   & {73,52}                             & {49,67}                             & {2,43}                                   & \textcolor{purple}{49,39} & \textcolor{purple}{73,19} & \textcolor{purple}{23,78} & \textcolor{purple}{13,06} & \textcolor{purple}{32,31} & \textcolor{purple}{34,64} \\
        {6}                           & {50}   & \textcolor{purple}{44,31}           & {45,07}                             & \textcolor{purple}{33,29}                & {\textbf{78,82}}          & {\textbf{90,22}}          & {\textbf{7,29}}           & \textcolor{purple}{12,72} & \textcolor{purple}{33,29} & \textcolor{purple}{32,99} \\
        {6}                           & {100}  & {\textbf{80,95}}                    & {\textbf{69,88}}                    & {\textbf{3,34}}                          & {62,2}                    & \textcolor{purple}{80,62} & \textcolor{purple}{19,88} & \textcolor{purple}{14,24} & \textcolor{purple}{32,36} & \textcolor{purple}{32,94} \\

@@

        {1}                           & {2}     & \textcolor{purple}{89,69}           & {93,68}                             & \textcolor{purple}{52,04}                & {88,09}                         & \textcolor{purple}{90,12}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,37}       & \textcolor{purple}{76,56}      \\
        {1}                           & {10}    & {96,31}                             & {94,21}                             & \textcolor{purple}{52,78}                & {90,6}                          & \textcolor{purple}{90,15}       & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,32}                  & \textcolor{purple}{76,52}      \\
        {1}                           & {16}    & {94,97}                             & \textcolor{purple}{92,8}            & \textcolor{purple}{52,78}                & {91,97}                         & {93,45}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{91,03}       & \textcolor{purple}{76,52}      \\
        {1}                           & {50}    & \textcolor{purple}{90,1}            & \textcolor{purple}{91,58}           & \textcolor{purple}{52,78}                & {94,66}                         & {93,39}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,41}       & \textcolor{purple}{76,52}      \\
        {1}                           & {100}   & {90,41}                             & \textcolor{purple}{92,66}           & \textcolor{purple}{52,78}                & \textcolor{purple}{83,03}       & \textcolor{purple}{90,23}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,72}       & \textcolor{purple}{76,52}      \\
        {2}                           & {2}     & {92,45}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,04}                & {88,72}                         & \textbf{94,38}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,89}       & \textcolor{purple}{76,56}      \\
        {2}                           & {10}    & {96,09}                             & \textbf{94,44}                      & \textcolor{purple}{52,78}                & {91,54}                         & \textcolor{purple}{90,71}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,54}       & \textcolor{purple}{76,52}      \\
        {2}                           & {16}    & {90,58}                             & \textcolor{purple}{92,66}           & \textcolor{purple}{52,78}                & \textbf{97,18}                  & {94,14}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,98}       & \textcolor{purple}{76,52}      \\
        {2}                           & {50}    & {89,28}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,78}                & {92,01}                         & {93,01}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,5}        & \textcolor{purple}{76,52}      \\
        {2}                           & {100}   & \textbf{98,91}                      & \textcolor{purple}{92,97}           & \textcolor{purple}{52,78}                & {92,66}                         & {92,49}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,68}       & \textcolor{purple}{76,52}      \\
        {3}                           & {2}     & {90,97}                             & {93,32}                             & \textcolor{purple}{52,04}                & {87,88}                         & {92,53}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{90,58}       & \textcolor{purple}{76,56}      \\
        {3}                           & {10}    & {97,01}                             & \textbf{{94,79}}                    & \textcolor{purple}{52,78}                & {94,4}                          & {92,8}                          & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,17}                  & \textcolor{purple}{76,52}      \\
        {3}                           & {16}    & {95,36}                             & {93,1}                              & \textcolor{purple}{52,78}                & {86,72}                         & {91,88}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,06}       & \textcolor{purple}{76,52}      \\
        {3}                           & {50}    & {90,93}                             & \textcolor{purple}{90,84}           & \textcolor{purple}{52,78}                & {94,92}                         & \textbf{94,18}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,59}       & \textcolor{purple}{76,52}      \\
        {3}                           & {100}   & \textcolor{purple}{89,37}           & \textcolor{purple}{90,76}           & \textcolor{purple}{52,78}                & {94,1}                          & {92,8}                          & \textcolor{purple}{49,74}      & {100}                           & \textbf{91,84}                  & \textcolor{purple}{76,52}      \\
        {4}                           & {2}     & {94,86}                             & \textcolor{purple}{92,11}           & \textcolor{purple}{52,04}                & {88,56}                         & {93,86}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,11}       & \textcolor{purple}{76,56}      \\
        {4}                           & {10}    & {90,58}                             & \textcolor{purple}{92,75}           & \textcolor{purple}{52,78}                & {95,05}                         & {93,71}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,89}       & \textcolor{purple}{76,52}      \\
        {4}                           & {16}    & \textbf{98,57}                      & {94,14}                             & \textcolor{purple}{52,78}                & \textbf{96,14}                  & \textbf{95,23}                  & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,06}       & \textcolor{purple}{76,52}      \\
        {4}                           & {50}    & {95,66}                             & {93,32}                             & \textcolor{purple}{52,78}                & {91,01}                         & \textcolor{purple}{90,45}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,85}       & \textcolor{purple}{76,52}      \\
        {4}                           & {100}   & \textcolor{purple}{89,41}           & {93,58}                             & \textcolor{purple}{52,78}                & {94,66}                         & {93,19}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{86,98}       & \textcolor{purple}{76,52}      \\
        {6}                           & {2}     & {93,39}                             & {92,94}                             & \textcolor{purple}{52,04}                & \textcolor{purple}{82,18}       & {92,16}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{90,05}       & \textcolor{purple}{76,56}      \\
        {6}                           & {10}    & \textbf{98,78}                      & \textbf{94,23}                      & \textcolor{purple}{52,78}                & \textbf{96,79}                  & {92,75}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{87,67}       & \textcolor{purple}{76,52}      \\
        {6}                           & {16}    & {96,96}                             & \textcolor{purple}{91,32}           & \textcolor{purple}{52,78}                & {95,57}                         & {93,75}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,37}       & \textcolor{purple}{76,52}      \\
        {6}                           & {50}    & \textcolor{purple}{88,28}           & \textcolor{purple}{91,45}           & \textcolor{purple}{52,78}                & {91,71}                         & \textcolor{purple}{86,24}       & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{88,32}       & \textcolor{purple}{76,52}      \\
        {6}                           & {100}   & {94,92}                             & \textcolor{purple}{92,45}           & \textcolor{purple}{52,78}                & {95,3}                          & {93,62}                         & \textcolor{purple}{49,74}      & {100}                           & \textcolor{purple}{89,19}       & \textcolor{purple}{76,52}      \\

>>>>

        {1}                           & {2}    & {70,49}                             & {54,73}                             & {7,29}                                   & {70,16}                & {85,06}                & {13,06}                & \textcolor{red}{11,68} & \textcolor{red}{32,25} & \textcolor{red}{34,03} \\
        {1}                           & {10}   & {78,26}                             & {63,33}                             & {3,56}                                   & {68,97}                & {85,01}                & {10,85}                & \textcolor{red}{12,72} & \textcolor{red}{32,77} & \textcolor{red}{33,85} \\
        {1}                           & {16}   & {74,18}                             & {52,21}                             & {5,38}                                   & {71,57}                & {86,87}                & {10,72}                & \textcolor{red}{13,19} & \textcolor{red}{33,64} & \textcolor{red}{33,33} \\
        {1}                           & {50}   & {70,83}                             & \textcolor{red}{43,56}              & {4,21}                                   & {65,23}                & {83,11}                & {12,54}                & \textcolor{red}{11,81} & \textcolor{red}{33,14} & \textcolor{red}{34,72} \\
        {1}                           & {100}  & {73,18}                             & {52,14}                             & {3,86}                                   & \textcolor{red}{60,94} & \textcolor{red}{80,85} & \textcolor{red}{20,36} & \textcolor{red}{13,67} & \textcolor{red}{33,71} & \textcolor{red}{33,64} \\
        {2}                           & {2}    & {72,31}                             & {50,42}                             & {5,52}                                   & {66,2}                 & {83,39}                & {14,42}                & \textcolor{red}{13,32} & \textcolor{red}{33,62} & \textcolor{red}{32,73} \\
        {2}                           & {10}   & {75,22}                             & {58,4}                              & {3,99}                                   & {73,22}                & {87,68}                & {9,03}                 & \textcolor{red}{12,37} & \textcolor{red}{33,3}  & \textcolor{red}{34,11} \\
        {2}                           & {16}   & {\textbf{81,64}}                    & {\textbf{73,66}}                    & {\textbf{2,86}}                          & {73,44}                & {88,21}                & {8,85}                 & \textcolor{red}{12,98} & \textcolor{red}{33,94} & \textcolor{red}{34,24} \\
        {2}                           & {50}   & {74,39}                             & {48,53}                             & {3,17}                                   & {\textbf{75,35}}       & \textbf{88,77}         & \textbf{8,07}          & \textcolor{red}{14,19} & \textcolor{red}{33,04} & \textcolor{red}{33,46} \\
        {2}                           & {100}  & {74,09}                             & {54,88}                             & {3,65}                                   & \textcolor{red}{54,56} & \textcolor{red}{76,95} & \textcolor{red}{22,57} & \textcolor{red}{13,28} & \textcolor{red}{32,8}  & \textcolor{red}{33,38} \\
        {3}                           & {2}    & {71,03}                             & {50,76}                             & {4,62}                                   & {65,18}                & \textcolor{red}{82,68} & {14,23}                & \textcolor{red}{12,76} & \textcolor{red}{33,58} & \textcolor{red}{33,64} \\
        {3}                           & {10}   & {76,91}                             & {59,42}                             & {2,6}                                    & {71,66}                & {87,14}                & {9,9}                  & \textcolor{red}{12,54} & \textcolor{red}{32,75} & \textcolor{red}{33,85} \\
        {3}                           & {16}   & {79,95}                             & {67,55}                             & {3,17}                                   & \textcolor{red}{50,13} & \textcolor{red}{73,24} & {24,22}                & \textcolor{red}{12,93} & \textcolor{red}{33,79} & \textcolor{red}{34,46} \\
        {3}                           & {50}   & {62,93}                             & {48,03}                             & {16,58}                                  & {\textbf{76,09}}       & {\textbf{88,5}}        & \textbf{9,2}           & \textcolor{red}{13,67} & \textcolor{red}{33,73} & \textcolor{red}{34,29} \\
        {3}                           & {100}  & {75,74}                             & {57,51}                             & {2,43}                                   & {69,7}                 & {86,14}                & {9,38}                 & \textcolor{red}{13,02} & \textcolor{red}{33,64} & \textcolor{red}{34,2}  \\
        {4}                           & {2}    & \textcolor{red}{41,23}              & \textcolor{red}{42,53}              & \textcolor{red}{35,33}                   & {63,93}                & \textcolor{red}{82,34} & {15,3}                 & \textcolor{red}{12,2}  & \textcolor{red}{33,25} & \textcolor{red}{33,64} \\
        {4}                           & {10}   & {78,99}                             & {66,4}                              & {2,08}                                   & {73,22}                & {88,01}                & {10,85}                & \textcolor{red}{12,5}  & \textcolor{red}{33,55} & \textcolor{red}{33,16} \\
        {4}                           & {16}   & {\textbf{80,08}}                    & {\textbf{70,48}}                    & {\textbf{3,47}}                          & {69,4}                 & {86,09}                & {10,63}                & \textcolor{red}{11,72} & \textcolor{red}{33,1}  & \textcolor{red}{34,03} \\
        {4}                           & {50}   & {75,48}                             & {54,44}                             & {3,34}                                   & {71,35}                & {86,61}                & {10,68}                & \textcolor{red}{11,81} & \textcolor{red}{33,18} & \textcolor{red}{34,33} \\
        {4}                           & {100}  & {74,78}                             & {57,09}                             & {3,86}                                   & \textcolor{red}{59,2}  & \textcolor{red}{80,14} & \textcolor{red}{20,57} & \textcolor{red}{12,67} & \textcolor{red}{32,3}  & \textcolor{red}{34,55} \\
        {6}                           & {2}    & {72,87}                             & {51,44}                             & {2,78}                                   & {60,82}                & \textcolor{red}{80,42} & {17,07}                & \textcolor{red}{13,45} & \textcolor{red}{33,73} & \textcolor{red}{33,64} \\
        {6}                           & {10}   & {73,61}                             & {48,73}                             & {2,82}                                   & \textcolor{red}{32,64} & \textcolor{red}{58,42} & \textcolor{red}{33,12} & \textcolor{red}{11,89} & \textcolor{red}{33,15} & \textcolor{red}{35,03} \\
        {6}                           & {16}   & {73,52}                             & {49,67}                             & {2,43}                                   & \textcolor{red}{49,39} & \textcolor{red}{73,19} & \textcolor{red}{23,78} & \textcolor{red}{13,06} & \textcolor{red}{32,31} & \textcolor{red}{34,64} \\
        {6}                           & {50}   & \textcolor{red}{44,31}              & {45,07}                             & \textcolor{red}{33,29}                   & {\textbf{78,82}}       & {\textbf{90,22}}       & {\textbf{7,29}}        & \textcolor{red}{12,72} & \textcolor{red}{33,29} & \textcolor{red}{32,99} \\
        {6}                           & {100}  & {\textbf{80,95}}                    & {\textbf{69,88}}                    & {\textbf{3,34}}                          & {62,2}                 & \textcolor{red}{80,62} & \textcolor{red}{19,88} & \textcolor{red}{14,24} & \textcolor{red}{32,36} & \textcolor{red}{32,94} \\

@@

        {1}                           & {2}     & \textcolor{red}{89,69}              & {93,68}                             & \textcolor{red}{52,04}                   & {88,09}                         & \textcolor{red}{90,12}          & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{87,37}          & \textcolor{red}{76,56}         \\
        {1}                           & {10}    & {96,31}                             & {94,21}                             & \textcolor{red}{52,78}                   & {90,6}                          & \textcolor{red}{90,15}          & \textcolor{red}{49,74}         & {100}                           & \textbf{91,32}                  & \textcolor{red}{76,52}         \\
        {1}                           & {16}    & {94,97}                             & \textcolor{red}{92,8}               & \textcolor{red}{52,78}                   & {91,97}                         & {93,45}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{91,03}          & \textcolor{red}{76,52}         \\
        {1}                           & {50}    & \textcolor{red}{90,1}               & \textcolor{red}{91,58}              & \textcolor{red}{52,78}                   & {94,66}                         & {93,39}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{89,41}          & \textcolor{red}{76,52}         \\
        {1}                           & {100}   & {90,41}                             & \textcolor{red}{92,66}              & \textcolor{red}{52,78}                   & \textcolor{red}{83,03}          & \textcolor{red}{90,23}          & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{86,72}          & \textcolor{red}{76,52}         \\
        {2}                           & {2}     & {92,45}                             & \textcolor{red}{92,45}              & \textcolor{red}{52,04}                   & {88,72}                         & \textbf{94,38}                  & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,89}          & \textcolor{red}{76,56}         \\
        {2}                           & {10}    & {96,09}                             & \textbf{94,44}                      & \textcolor{red}{52,78}                   & {91,54}                         & \textcolor{red}{90,71}          & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{89,54}          & \textcolor{red}{76,52}         \\
        {2}                           & {16}    & {90,58}                             & \textcolor{red}{92,66}              & \textcolor{red}{52,78}                   & \textbf{97,18}                  & {94,14}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{86,98}          & \textcolor{red}{76,52}         \\
        {2}                           & {50}    & {89,28}                             & \textcolor{red}{92,45}              & \textcolor{red}{52,78}                   & {92,01}                         & {93,01}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{86,5}           & \textcolor{red}{76,52}         \\
        {2}                           & {100}   & \textbf{98,91}                      & \textcolor{red}{92,97}              & \textcolor{red}{52,78}                   & {92,66}                         & {92,49}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{86,68}          & \textcolor{red}{76,52}         \\
        {3}                           & {2}     & {90,97}                             & {93,32}                             & \textcolor{red}{52,04}                   & {87,88}                         & {92,53}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{90,58}          & \textcolor{red}{76,56}         \\
        {3}                           & {10}    & {97,01}                             & \textbf{{94,79}}                    & \textcolor{red}{52,78}                   & {94,4}                          & {92,8}                          & \textcolor{red}{49,74}         & {100}                           & \textbf{91,17}                  & \textcolor{red}{76,52}         \\
        {3}                           & {16}    & {95,36}                             & {93,1}                              & \textcolor{red}{52,78}                   & {86,72}                         & {91,88}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,06}          & \textcolor{red}{76,52}         \\
        {3}                           & {50}    & {90,93}                             & \textcolor{red}{90,84}              & \textcolor{red}{52,78}                   & {94,92}                         & \textbf{94,18}                  & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,59}          & \textcolor{red}{76,52}         \\
        {3}                           & {100}   & \textcolor{red}{89,37}              & \textcolor{red}{90,76}              & \textcolor{red}{52,78}                   & {94,1}                          & {92,8}                          & \textcolor{red}{49,74}         & {100}                           & \textbf{91,84}                  & \textcolor{red}{76,52}         \\
        {4}                           & {2}     & {94,86}                             & \textcolor{red}{92,11}              & \textcolor{red}{52,04}                   & {88,56}                         & {93,86}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{87,11}          & \textcolor{red}{76,56}         \\
        {4}                           & {10}    & {90,58}                             & \textcolor{red}{92,75}              & \textcolor{red}{52,78}                   & {95,05}                         & {93,71}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{89,89}          & \textcolor{red}{76,52}         \\
        {4}                           & {16}    & \textbf{98,57}                      & {94,14}                             & \textcolor{red}{52,78}                   & \textbf{96,14}                  & \textbf{95,23}                  & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,06}          & \textcolor{red}{76,52}         \\
        {4}                           & {50}    & {95,66}                             & {93,32}                             & \textcolor{red}{52,78}                   & {91,01}                         & \textcolor{red}{90,45}          & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,85}          & \textcolor{red}{76,52}         \\
        {4}                           & {100}   & \textcolor{red}{89,41}              & {93,58}                             & \textcolor{red}{52,78}                   & {94,66}                         & {93,19}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{86,98}          & \textcolor{red}{76,52}         \\
        {6}                           & {2}     & {93,39}                             & {92,94}                             & \textcolor{red}{52,04}                   & \textcolor{red}{82,18}          & {92,16}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{90,05}          & \textcolor{red}{76,56}         \\
        {6}                           & {10}    & \textbf{98,78}                      & \textbf{94,23}                      & \textcolor{red}{52,78}                   & \textbf{96,79}                  & {92,75}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{87,67}          & \textcolor{red}{76,52}         \\
        {6}                           & {16}    & {96,96}                             & \textcolor{red}{91,32}              & \textcolor{red}{52,78}                   & {95,57}                         & {93,75}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{89,37}          & \textcolor{red}{76,52}         \\
        {6}                           & {50}    & \textcolor{red}{88,28}              & \textcolor{red}{91,45}              & \textcolor{red}{52,78}                   & {91,71}                         & \textcolor{red}{86,24}          & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{88,32}          & \textcolor{red}{76,52}         \\
        {6}                           & {100}   & {94,92}                             & \textcolor{red}{92,45}              & \textcolor{red}{52,78}                   & {95,3}                          & {93,62}                         & \textcolor{red}{49,74}         & {100}                           & \textcolor{red}{89,19}          & \textcolor{red}{76,52}         \\
